DisCon Kids Pilot

### 2019-03-01 analysis/02_kids_600.Rmd
update kids analysis file

@@

data %>%
  filter(phase != "training") %>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(subage,mean,bf) %>%
  knitr::kable(digits = 3)

samples = ttestBF(x$correct, mu = 1/3, posterior = T, iterations = 1000)

@@

mean(model_data$age_num)

>>>>

library(coda)
library(reshape2)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

@@

data %>%
  filter(phase != "training") %>%
  group_by(subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(mean,bf) %>%
  knitr::kable(digits = 3)

# BAyesian t-test by age group

data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(mean= mean(unlist(correct)),
         bf = extractBF(ttestBF(unlist(correct), mu = 1/3))$bf) %>%
  select(subage,mean,bf) %>%
  knitr::kable(digits = 3)

```
Plotting posterior based on t-test

```{r}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 10000)[,"mu"])))%>%
  select(-correct)

plot_dens_ci <- plot_post %>%
  summarise(mode = estimate_mode(unlist(posterior)),
            lci = hdi_lower(unlist(posterior)),
            uci = hdi_upper(unlist(posterior)))

#### make density plot ?

plot_dens <- data_frame(
  age = rep(c(3,4), each = 10000),
  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)

densities <- plot_dens %>%
  group_by(age) %>%
  do(., dens = density(.$posterior))

densities_df <-
  data.frame(
    age = c(rep('3', 512),
              rep('4', 512)),
    x = c(densities$dens[[1]]$x, 
          densities$dens[[2]]$x),
    y = c(densities$dens[[1]]$y,
          densities$dens[[2]]$y)
  ) %>%
  group_by(age)%>%
  mutate (
    ci_shade = ifelse( age == "3",
      ifelse( x <= plot_dens_ci%>%filter(subage == "3")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "3")%>%pull(uci), "OFF", "ON"), ifelse( x <= plot_dens_ci%>%filter(subage == "4")%>%pull(lci) | x >= plot_dens_ci%>%filter(subage == "4")%>%pull(uci), "OFF", "ON")))

ggplot(plot_dens, aes(posterior, group = factor(age))) +
  geom_density(alpha = .5)+
  geom_vline(xintercept = 1/3, lty=2)+
  geom_area(data = densities_df %>% filter(ci_shade == "ON"), aes(x = x, y = y, fill = age), alpha = .5) + 
  labs(x="Proportion Correct")+
  theme_few() +
  xlim(-0.05,1.05)+
  guides(alpha = F)+
  scale_fill_solarized(name = "Age")+
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

@@

### 2019-03-01 analysis/02_kids_power_analysis_600.Rmd
update kids analysis file

>>>>

# Bayesian Power analysis

```{r}
N           <- 1000  # Number of MC reps
n           <- 20  # Sample size
sigma       <- 0.3    # Error standard devation

true_mu     <- (0.5785714-1/3)	  # True value of mu

pri.mn.anal <- 0    # Prior for mu
pri.sd.anal <- Inf

 L <- rep(0,N)
 U <- rep(0,N)

 set.seed(0820)

 for(rep in 1:N){

  #Generate data:
    Y  <- rnorm(n,true_mu,sigma)

   #Compute posterior 95% interval:
    post.var <- 1/(n/sigma^2+1/pri.sd.anal^2)
    post.mn  <- post.var*(pri.mn.anal/pri.sd.anal^2+sum(Y)/sigma^2)
    L[rep]   <- post.mn-1.96*sqrt(post.var)
    U[rep]   <- post.mn+1.96*sqrt(post.var)
 }

plot(NA,xlim=c(-1,1),ylim=c(1,N),xlab="95% interval",ylab="Replication")
abline(v=0)

for(rep in 1:N){
    reject <- L[rep]>0 | U[rep]<0
    lines(c(L[rep],U[rep]),c(rep,rep),col=ifelse(reject>0,2,1))
}

 mean(L>0 | U<0)
```
